Distributed Environment for Auctioning Virtual Power System Resources

### 2022-02-04 other/paper-aicts-chekan.tex
Reduced 1 page with tail suppression.

The current trends in energy sector organizations in the developed countries (including Russia) pay special attention to the concept of ``smart energy.'' The environmental and economic situation forces them to optimize energy processes, switch to alternative sources, and introduce smart grids [1]. Information technologies play a special role in this process as a base for implementing a ``smart energy'' control. In this regard, the issue of training specialists with a comprehensive understanding of energy processes as being based on modern technologies is relevant. On the other hand, smart energy has not yet found good distribution at the household level in some countries. One of the effective methods for dealing with these issues is devising tools for specialized training of young specialist-engineers. The proposed game component plays an essential role in the educational effect, an energetic auction modeling tool as additional didactic material~[2].

@@

The powerstand game session consists of stages. One of the stages is auctions for the ownership of objects of the conditional microdistrict assembled by the participants of the power grid. The obtained grid is subsequently modeled for energy efficiency and profitability. Since the set of objects directly impacts the simulation result, it is crucial to reliably and promptly carry out this stage of work with the stand. The problem is the imperfection of the manual auction version when the host independently collects the participants' bids using material (paper) or digital media (messages in messenger applications). We proposed automating this work stage and introducing it into the existing software packages to reduce costs and improve reliability. Power system modeling is an already essentially automated process. Reducing external dependencies through additional automation will increase the integrity of the software and hardware complex and increase the dynamism of the activities carried out on it, as well as reduce the requirements for operator qualification, which is especially important when deploying the stand as an educational tool at various sites where the direct presence of administrators and developers is not expected.

@@

There is no consensus on the issue of organizing a network infrastructure, namely, connecting services, and most typically, services interact through open channels using standardized TCP and UDP protocols. This option provides sufficient throughput and, in the case of TCP, consistent two-way communication but imposes security and network infrastructure requirements. Problems regarding network infrastructure most frequently lie in the configuration of routing and access ports, and security issues are addressed through various add-ons related to encryption and authorization mechanisms. The most popular access control protocol at present is OAuth [10]. There are ready-made solutions [11] that implement interaction using this protocol. Also, to protect applications from denial of service attacks, balancers are used, in particular, NGINX [12].

At the same time, there are scenarios where it is necessary to block access to the application from the external network to everyone except trusted nodes. It is especially true for corporate systems. To implement such scenarios, VPN tunneling, access via a terminal connection (for example, VNC), and web interface publishing via HTTPS [13] are often used, and the latter method is the most desirable, according to the author of the source. At the same time, VPN tunneling is considered the most popular and common method of creating a closed channel between nodes. However, its use is associated with some risks and requires proper configuration. The same applies to a web application, which will require additional labor to implement. The terminal connection is used mainly for organizing user interaction with the desktop (VNC is used for this). At the same time, the SSH protocol, in addition to its primary functionality - remote interaction with the user environment - provides tunneling of TCP connections over an encrypted channel [14]. To organize a simple SSH tunnel, two nodes are enough, where an SSH server is installed on one, and an SSH client is installed on the second, launched with a specific set of arguments. Both components come standard with many Linux distributions [15]. The further configuration depends on security and infrastructure requirements.

@@

The auction, as mentioned above, the module has become a prototype of the distributed environment. Being a part of a powerstand software, the module is used in educational institutions, engineering competitions, and intensive programs. During the powerstand operation and administration and personal observation of auction system operation, a significant amount of user experience was accumulated, based on decisions made regarding developing new versions of software products and creating unique technical solutions. This experience has become the primary source of expertise in forming requirements for a new interpretation of the auction system in distributed scenarios.

Three events made the dominant contribution to the expertise. This section will describe them and briefly analyze the user experience.

@@

Given the conditions for revenue equivalence, we can consider an all-pay auction to be equivalent to a sealed-bid first-price auction in terms of determining value. By bidding on the limit value, the participants set the personal value of the object, sacrificing its objective value (economic effect). To resolve the disputable situation, the personal value is determined again by bidding on the amount of money the participant is willing to give to own the object. Since the increase in this value negatively affects the final result of the participants, it was decided not to apply the "catch-up" bets rule in all-pay, holding a second round only if the leading bets completely match.

@@

The system layer provides the infrastructure for connecting servers by SSH tunnel-based port forwarding. As mentioned, tunneling TCP connections via SSH does not require complex configuration. In particular, the OpenSSH server and client are included in the standard system software of a wide range of Linux distributions, and the ease of configuration makes this tool a suitable solution for building network applications with a distributed architecture. The construction of architecture on SSH tunnels is described in more detail in [7]. Since the SSH protocol supports key-based authorization, this method allows to set up a secure, stable communication channel between network nodes and explicitly define the connection topology. This solution is expected to provide sufficient reliability while meeting the minimum guaranteed transfer speed. It also simplifies the implementation of server programs (because only a connection to a local port is needed) and provides the ability to debug the entire system on a single computer.

@@

Three applications constitute a three-tier client-server architecture in the software layer: the core (cloud level), the relay, and the mediator (terminal level). We consider the user interface a separate entity interacting with the mediator and the administrator interface interacting with a particular HTTP endpoint of the core. The core server controls the game session logic and accepts connections from the relays, updating the current session state for them and processing incoming commands from the players. The relay server is designed to reduce the load on the network and optimize the interaction between participants and the core using replication and time amortization. The mediator server keeps a copy of the state and projects it into a suitable form for processing by the UI. Thus, the tasks of authorization and identification are performed entirely by tunnels and the mediator. In the interface, it is necessary to implement only the display of data and the transmission of commands to the kernel through the mediator using a simple API.

@@

In the current iteration, it is decided that player identification is carried out by mediator settings built into the system configuration. In the future, it is possible to implement authorization and identification by passwords or IP addresses (which will require eliminating tunnels between relays and mediators).

All three programs are launched for greater stability at the system level as Systemd services configured to automatically restart upon a critical error. From the server-side, a sudden disconnection of the client should not incur problems because protocols provide state synchronization, and messages about the players’ actions are not necessary for the continuation of the game session.

@@

The developed auction environment was tested at events as part of the third version of the STIES stand. From autumn 2019 to spring 2021, the powerstand was used at two all-Russian events, which are the finals of the "Intelligent Energy Systems" profile of the NTI Kruzhok Movement Olympiad (currently referred to as NTO) in 2020 and 2021, respectively. These activities allowed to perform live testing of the auction environment in the conditions of intense engineering competition to personally observe the user experience, which made it possible to identify the weak and strong points of the developed system and identify areas for further research and development.

\subsection{Distributed scenario}
\label{sec:eval-distr}

The final “Intelligent Energy Systems” profile of the NTO in 2020 was held from March 10 to 14. 60 schoolchildren from different cities of Russia, united in 13 teams, competed in a shared virtual environment while physically being in three different places:
school №709 Moscow (4 teams),
Tyumen State University (5 teams),
Novosibirsk State Technical University (4 teams).
It is worth noting that this was the first approbation of the updated auction system, and the specified configuration is the maximum on which the powerstand has ever been operated. The testing was successful. Thanks to the optimized architecture, the delays between state changes averaged no more than 1 second due to the processing of the JSON packet in the web interface. The peak delay was about 3 seconds, caused by problems with the Internet channel at the Novosibirsk site.

\subsection{High-load local scenario}
\label{sec:eval-high}

From March 29 to April 3, 2021, Tyumen State University hosted the finals of the "Intelligent Energy Systems" profile of the NTO. 10 teams took part in this final. But due to organizational difficulties, all teams were placed on the same site. It meant the need to configure a set of stands for 10 participants. It became the primary technical challenge of the event. So, 4 stands were set up (and, accordingly, 4 servers), the game core and auction relay were placed on one of these servers, the rest of the necessary components were placed on the rest. All computers (4 servers and 10 terminals) were connected to the same physical network with a router.

@@

Investigated auction simulators are based on an entertaining game component and have no direct customization. One class is mobile games, e.g., Bid Wars [27], whereas auction simulators are frequently built into the existing game model as a side mechanic. Multiplayer online games [28] are examples of simulation. An aggravating factor in the compliance of analogs with the set requirements is a fixed model of conducting, most often corresponding to the English auction, when bids are announced openly, and the auction for the lot is conducted until there are no new bids.

@@

Thus, the choice of architecture implementation at this stage is considered justified, taking all positive and negative factors into account. Nevertheless, it makes sense to apply developments to increase the speed and reduce delays in SSH tunneling [31, 32]. Alternatively, even abandon SSH tunnels in favor of other transport protocols, such as a Secure WebSocket with a well-built authorization. It will assume the complexity additions to the software layer but is considered in the future.

Another class of problems is the user interface, its connection with the mediator using an HTTP polling with a JSON response. Although a near-second delay for JSON deserializing does not affect the auction’s perception and dynamics with a fast network channel, this is currently a bottleneck when transferring data to the interface. The solution to this problem could be to use CBOR instead of JSON or implement WebSockets communication, making it possible to eliminate the mediator as an extra intermediate link. Despite this, JavaScript has less performance than Haskell (being an interpreted language), and the use of a mediator for intermediate marshaling is justified at the current stage. However, it creates problems with CORS when accessing localhost from a non-local domain [33], which in our case hosts the user interface. The workaround here is to disable CORS when accessing the UI, but replacing the mediator with direct access to the interface is considered an assumption in conjunction with the above.

>>>>

The current trends in energy sector organizations in the developed countries (including Russia) pay special attention to the concept of ``smart energy.'' The environmental and economic situation forces them to optimize energy processes, switch to alternative sources, and introduce smart grids [1]. Information technologies play a special role here as implementers of a ``smart energy'' control. In this regard, the issue of training specialists with a comprehensive understanding of energy processes as being based on modern technologies is relevant. On the other hand, smart energy has not yet found good distribution at the household level in some countries. One of the effective methods for dealing with these issues is devising tools for specialized training of young specialist-engineers. The proposed game component plays an essential role in the educational effect, an energetic auction modeling tool as additional didactic material~[2].

@@

The powerstand game session consists of stages. One of the stages is auctions for the ownership of objects of the conditional microdistrict assembled by the participants of the power grid. The grid is subsequently simulated, accounting parameters of energy efficiency and profitability. Since the set of objects directly impacts the simulation result, it is crucial to carry out reliably and promptly this stage of work with the stand. The problem is the imperfection of the manual auction version when the hosts independently collect the participants' bids using material (paper) or digital media (messages in a messenger application). We proposed automating this stage and introducing it into the existing software packages to improve reliability. Power system modeling is an already essentially automated process. Reducing external dependencies through additional automation will increase the integrity of the software and hardware complex and increase the dynamics of the activities, as well as reduce the requirements for operator qualification requirements, which is especially important when deploying the stand as an educational tool at various sites where the direct presence of administrators is not expected.

@@

There is no consensus on the issue of organizing a network infrastructure, namely, connecting services, and most typically, services interact through open channels using TCP and UDP protocols. This option provides sufficient throughput and, in the case of TCP, consistent two-way communication but imposes security and network infrastructure requirements. Problems regarding network infrastructure most frequently lie in the configuration of routing and access ports, and security issues are addressed through various add-ons related to encryption and authorization mechanisms. The most popular access control protocol at present is OAuth [10]. There are ready-made solutions [11] that implement interaction using this protocol. To protect applications from denial of service attacks, balancers are used, \emph{e.g.}, NGINX [12].

There are scenarios where it is necessary to block access to the application from the external network to everyone except trusted nodes, namely, in corporate systems. To implement such scenarios, VPN tunneling, access via a terminal connection (for example, VNC), and web interface publishing via HTTPS [13] are often used, and the latter method prevails by author's opinion. VPN tunneling is considered the most popular and common method of creating a closed channel between nodes. However, its use is associated with some risks and requires proper configuration. The same applies to a web application. The terminal connection is used mainly for organizing user interaction with the desktop (VNC is used for this). At the same time, the SSH protocol, in addition to its primary functionality - remote interaction with the user environment - provides tunneling of TCP connections over an encrypted channel [14]. To organize a simple SSH tunnel, two nodes are enough, where an SSH server is installed on one, and an SSH client is installed on the second, launched with a specific set of arguments. Both components come standard with many Linux distributions [15]. The further configuration depends on security and infrastructure requirements.

@@

The auction, as mentioned above, the module has become a prototype of the distributed environment. Being a part of a powerstand software, the module is used in educational institutions, engineering competitions, and intensive programs. During the powerstand operation and administration and personal observation of auction system operation, a significant amount of user experience was accumulated, based on decisions made regarding developing new versions of software products and creating unique technical solutions. This experience has become the primary source of expertise in forming requirements for a new interpretation of the auction system in distributed scenarios. Three events made the dominant contribution to the expertise. This section will describe them and briefly analyze the user experience.

@@

Given the conditions for revenue equivalence, we can consider an all-pay auction to be equivalent to a sealed-bid first-price auction in determining value. By bidding on the limit value, the participants set the personal value of the object, sacrificing its objective value (economic effect). To resolve the disputable situation, the personal value is determined again by bidding on the amount the participant is willing to give to own the object. Since the increase in this value negatively affects the final result of the participants, it was decided not to apply the ``catch-up'' bets rule in all-pay, holding a second round only if the leading bets completely match.

@@

The system layer provides the infrastructure for connecting servers by SSH tunnel-based port forwarding. Tunneling TCP connections via SSH does not require complex configuration. In particular, the OpenSSH server and client are included in the standard system software of a wide range of Linux distributions, and the ease of configuration makes this tool a suitable solution for building network applications with a distributed architecture [7]. Since the SSH protocol supports key-based authorization, this method allows to set up a secure, stable communication channel between network nodes and explicitly define the connection topology. This solution is expected to provide sufficient reliability while meeting the minimum guaranteed transfer speed. It also simplifies the implementation of server programs (because only a connection to a local port is needed) and provides the ability to debug the entire system on a single computer.

@@

Three applications constitute a three-tier client-server architecture in the software layer: the core (cloud level), the relay, and the mediator (terminal level). The user interface is a separate entity interacting with the mediator and the administrator interface interacting with a particular HTTP endpoint of the core. The core server controls the game session logic and accepts connections from the relays, updating the current session state for them and processing incoming commands from the players. The relay server is designed to reduce the load on the network and optimize the interaction between participants and the core using replication and time amortization. The mediator server keeps a copy of the state and projects it into a suitable form for processing by the UI. Thus, the tasks of authorization and identification are performed entirely by tunnels and the mediator. In the interface, we implemented only the display of data and the transmission of commands to the kernel through the mediator using an API.

@@

As of today, player identification is carried out by mediator settings built into the system configuration. In the future, it is possible to implement authorization and identification by passwords or IP addresses (it requires eliminating tunnels between relays and mediators).

All three programs are launched at the system level as Systemd services configured to automatically restart upon a critical error. From the server-side, a sudden disconnection of a client should not incur problems because protocols provide state synchronization, and messages about the players’ actions are not necessary for the continuation of the game session.

@@

The developed auction environment was tested at events as part of the third version of the STIES stand. From autumn 2019 to spring 2021, the powerstand was used at two all-Russian events, which are the finals of the ``Intelligent Energy Systems'' profile of the NTI Kruzhok Movement Olympiad (referred to as NTO) in 2020 and 2021, respectively. These activities allowed to perform live testing of the auction environment in the conditions of intense engineering competition to personally observe the user experience, which made it possible to identify the weak and strong points of the developed system and identify areas for further research and development.

\paragraph{Distributed scenario}
\label{sec:eval-distr}
The final “Intelligent Energy Systems” profile of the NTO in 2020 was held from March 10 to 14. 60 schoolchildren from different cities of Russia, united in 13 teams, competed in a shared virtual environment while physically being in three different places:
school №709 Moscow (4 teams),
Tyumen State University (5 teams),
Novosibirsk State Technical University (4 teams).
It is worth noting that this was the first approbation of the updated auction system, and the specified configuration is the maximum on which the powerstand has ever been operated. The testing was successful. Thanks to the optimized architecture, the delays between state changes averaged no more than 1 second due to the processing of the JSON packet in the web interface. The peak delay was about 3 seconds, caused by problems with the Internet channel at the Novosibirsk site.

\paragraph{High-load local scenario}
\label{sec:eval-high}
From March 29 to April 3, 2021, Tyumen State University hosted the finals of the "Intelligent Energy Systems" profile of the NTO. 10 teams took part in this final. But due to organizational difficulties, all teams were placed on the same site. It meant the need to configure a set of stands for 10 participants. It became the primary technical challenge of the event. So, 4 stands were set up (and, accordingly, 4 servers), the game core and auction relay were placed on one of these servers, the rest of the necessary components were placed on the rest. All computers (4 servers and 10 terminals) were connected to the same physical network with a router.

@@

Investigated auction simulators are based on an entertaining game component and have no direct customization. One class is mobile games, \emph{e.g}., Bid Wars~[27], whereas auction simulators are frequently built in the game model as a side mechanic. Multiplayer online games [28] are such examples. An aggravating factor in the compliance of analogs with the set requirements is a fixed model of conducting, most often corresponding to the English auction, when bids are announced openly, and the auction for the lot is conducted until there are no new bids.

@@

Thus, the choice of architecture implementation at this stage is considered justified, taking all factors into account. Nevertheless, it makes sense to apply developments to increase the speed and reduce delays in SSH tunneling [31,32]. Alternatively, even abandon SSH tunnels in favor of other transport protocols, such as a Secure WebSocket with a well-built authorization. It will assume the complexity additions to the software layer but is considered in the future.

Another class of problems is the user interface, its connection with the mediator using an HTTP polling with a JSON response. Although a near-second delay for JSON deserializing does not affect the auction’s perception and dynamics with a fast network channel, this is currently a bottleneck when transferring data to the interface. The solution to this problem is to use CBOR instead of JSON or implement WebSockets communication, making it possible to eliminate the mediator as an extra intermediate link. Despite this, JavaScript has less performance than Haskell (being an interpreted language), and the use of a mediator for intermediate marshaling is justified at the current stage. However, it creates problems with CORS when accessing localhost from a non-local domain [33], which in our case hosts the user interface. The workaround here is to disable CORS when accessing the UI, but replacing the mediator with direct access to the interface is considered an assumption in conjunction with the above.
